An enhancer code compendium of early human neuronal and neural crest development

### 2025-05-15 manuscript.tex
Update author & acknowledgments

\title{An enhancer code compendium of early human neural and neural crest development}
\date{}

@@

\author[1,2,3,\orcidlink{0000-0001-7907-1247}]{Seppe De Winter}
\author[1,2,3,4,\orcidlink{0000-0002-1318-2603}]{Camiel Mannens}
\author[1,2,3,\orcidlink{0000-0002-5024-8691}]{Valerie Christiaens}
\author[1,2,3,\orcidlink{0000-0002-0876-2179}]{Roel Vandepoel}
\author[4,\orcidlink{0000-0003-1869-0372}]{Lijuan Hu}
\author[5,6,7,\orcidlink{0000-0002-2628-7834}]{Ruth M. Williams}
\author[5,6,\orcidlink{0000-0001-9289-0263}]{Tatjana Sauka-Spengler}
\author[4,\orcidlink{0000-0002-3491-3444}]{Sten Linnarsson}
\author[1,2,3,*,\orcidlink{0000-0002-8006-0315}]{Stein Aerts}

@@

\affil[1]{VIB Center of AI \& computational Biology, Leuven, Belgium}
\affil[2]{VIB-KU Leuven Center for Brain and Disease Research, Leuven, Belgium}
\affil[3]{KU Leuven Department of Human Genetics, Leuven, Belgium}
\affil[4]{Karolinska Institute, Department of Biochemistry and Biophysics, Stockholm, Sweden}
\affil[5]{Stowers Institute for Medical Research, Kansas City, Missouri, United States of America}
\affil[6]{University of Oxford, MRC Weatherall Institute of Molecular Medicine, Radcliffe Department of Medicine, Oxford, United Kingdom}
\affil[7]{University of Manchester, Faculty of Biology, Medicine and Health, Manchester, United Kingdom}

@@

We thank Peter L\"onnerberg for preprocessing the human embryo data and making it available through EGA.

@@

\begin{itemize}
  \item Conceptualization: S.D.W. \& S.A.
  \item Experiments and sample preparation: S.D.W., V.C., L.H., C.M., R.M.W., \& R.V.P.
  \item Computational analysis: S.D.W. \& C.M.
  \item Writing – original draft: S.D.W., C.M. \& S.A.
  \item Writing – review \& editing: S.D.W., C.M. \& S.A.
\end{itemize}

>>>>

\title{An enhancer code compendium of early human neuronal and neural crest development}
\date{}

@@

\author[1,2,3,\orcidlink{0000-0001-7907-1247}]{Seppe De Winter}
\author[1,2,3,4,\orcidlink{0000-0002-1318-2603}]{Camiel Mannens}
\author[1,2,3,\orcidlink{0000-0002-5024-8691}]{Valerie Christiaens}
\author[1,2,3,\orcidlink{0000-0002-0876-2179}]{Roel Vandepoel}
\author[4,\orcidlink{0000-0003-1869-0372}]{Lijuan Hu}
\author[4,\orcidlink{0000-0002-3491-3444}]{Sten Linnarsson}
\author[1,2,3,*,\orcidlink{0000-0002-8006-0315}]{Stein Aerts}

@@

\affil[1]{VIB Center of AI \& computational Biology, Leuven, Belgium}
\affil[2]{VIB-KU Leuven Center for Brain and Disease Research, Leuven, Belgium}
\affil[3]{KU Leuven Department of Human Genetics, Leuven, Belgium}
\affil[4]{Karolinska Institute, Department of Biochemistry and Biophysics, Stockholm, Sweden}

@@

We thank Peter L\"onnerberg for preprocessing the human embryo data and making it available through EGA.
We also thank Prof. Dr. Tatjana Sauka-Spengler and Dr. Ruth Williams for their great support with helping setting up the chicken embryo enhancer reporter assays.
Computing was performed at the Vlaamse Supercomputer Center and VIB datacore. 
This work was funded by the following grants to 
S. Aerts , %TODO: Add funding
PhD fellowship from FWO to S. De Winter (1191323N) and 
Post doctoral fellowship from ... to C. Mannens (), %TODO: add funding

@@

\begin{itemize}
  \item Conceptualization: S.D.W. \& S.A.
  \item Experiments and sample preparation: S.D.W., V.C., L.H., C.M., \& R.V.P.
  \item Computational analysis: S.D.W. \& C.M.
  \item Writing – original draft: S.D.W., C.M. \& S.A.
  \item Writing – review \& editing: S.D.W., C.M. \& S.A.
\end{itemize}
